\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-06-19 SuppMat.tex

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{adjustbox}   
%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%%%%%%%%%%%%%%%%%%%%%%%%%formatting cells colors
\usepackage[table,x11names,dvipsnames]{xcolor}
 \usepackage{collcell}
 \usepackage{array}
 \usepackage{tikz}
  \usepackage{pgfkeys}
 \usepackage{graphicx}
 \usepackage{amsmath,amssymb}

 \pgfkeys{/heat/.is family, /heat,
      Max colour/.initial = Green4,
      Min colour/.initial = Red1,
      max colour/.initial = SpringGreen3,
      mid colour/.initial = white,
      min colour/.initial = Yellow1,
      text colour/.initial = black,
      Min color/.style = {Min colour=#1},% for our friends who can't spell
      Max color/.style = {Max colour=#1},
      min color/.style = {min colour=#1},
      mid color/.style = {mid colour=#1},
      max color/.style = {max colour=#1},
      text color/.style = {text colour=#1},
      min/.initial = -1,
      mid/.initial = 0,
      max/.initial = 1,
      slider/.code={%
         \tikz{\shade[left color=\HVal{min colour},%
                      right color=\HVal{max colour}]%
            (current page.south west) rectangle ++(#1,12pt);
         }%
      }%
  }
  \newcommand\Heatset[1]{\pgfkeys{/heat, #1}}
  \newcommand\HVal[1]{\pgfkeysvalueof{/heat/#1}}

  \newcolumntype{H}{>{\collectcell\Heat}r<{\endcollectcell}}
  \newcommand\Heat[1]{% \Heat{number in the interval [min, max] }
    \if\relax\detokenize{#1}\relax% empty cell
    \else%
      \pgfmathparse{int(100*(#1-\HVal{min})/(\HVal{max}-\HVal{min}))}% map number to [0,100]
      \ifnum\pgfmathresult>100% too big
        \edef\HeatCell{\noexpand\cellcolor{\HVal{Max colour}}}%
      \else\ifnum\pgfmathresult<0% too small
          \edef\HeatCell{\noexpand\cellcolor{\HVal{Min colour}}}%
      \else\ifnum\pgfmathresult<50% between min and mid
	      \pgfmathparse{int(2*\pgfmathresult)}% map number to [0,100]
		  \edef\HeatCell{\noexpand\cellcolor{\HVal{mid colour}!\pgfmathresult!\HVal{min colour}}}%
		\else% between min and max
	      \pgfmathparse{int(2*(\pgfmathresult-50))}% map number to [0,100]
          \edef\HeatCell{\noexpand\cellcolor{\HVal{max colour}!\pgfmathresult!\HVal{mid colour}}}%
        \fi%
        \fi%
      \fi%
      \HeatCell\textcolor{\HVal{text colour}}{$#1$}%
    \fi%
  }

 \pgfkeys{/heatsec/.is family, /heatsec,
	Max colour/.initial = Green4,
	Min colour/.initial = Red1,
	max colour/.initial = SpringGreen3,
	mid colour/.initial = white,
	min colour/.initial = Yellow1,
	text colour/.initial = black,
	Min color/.style = {Min colour=#1},% for our friends who can't spell
	Max color/.style = {Max colour=#1},
	min color/.style = {min colour=#1},
	mid color/.style = {mid colour=#1},
	max color/.style = {max colour=#1},
	text color/.style = {text colour=#1},
	min/.initial = -1,
	mid/.initial = 0,
	max/.initial = 1,
	slider/.code={%
		\tikz{\shade[left color=\HVal{min colour},%
			right color=\HVal{max colour}]%
			(current page.south west) rectangle ++(#1,12pt);
		}%
	}%
}
\newcommand\HeatSecset[1]{\pgfkeys{/heatsec, #1}}
\newcommand\HSVal[1]{\pgfkeysvalueof{/heatsec/#1}}

\colorlet{BadCol}{Burlywood1!70!red}

\newcolumntype{S}{>{\collectcell\HeatSec}r<{\endcollectcell}}
\newcommand\HeatSec[1]{% \Heat{number in the interval [min, max] }
	\if\relax\detokenize{#1}\relax% empty cell
	\else%
	\pgfmathparse{int(100*(#1-\HSVal{min})/(\HSVal{max}-\HSVal{min}))}% map number to [0,100]
	\ifnum\pgfmathresult>100% too big
	\edef\HeatCell{\noexpand\cellcolor{\HSVal{Max colour}}}%
	\else\ifnum\pgfmathresult<0% too small
	\edef\HeatCell{\noexpand\cellcolor{\HSVal{Min colour}}}%
	\else\ifnum\pgfmathresult<50% between min and mid
	\pgfmathparse{int(2*\pgfmathresult)}% map number to [0,100]
	\edef\HeatCell{\noexpand\cellcolor{\HSVal{mid colour}!\pgfmathresult!\HSVal{min colour}}}%
	\else% between min and max
	\pgfmathparse{int(2*(\pgfmathresult-50))}% map number to [0,100]
	\edef\HeatCell{\noexpand\cellcolor{\HSVal{max colour}!\pgfmathresult!\HSVal{mid colour}}}%
	\fi%
	\fi%
	\fi%
	\HeatCell\textcolor{\HSVal{text colour}}{$#1$}%
	\fi%
}

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{todonotes}
\title{Supplementary materials}
%\author{}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed 
\newcommand{\Software}[1]{\texttt{#1}}
\newcommand{\OurTool}{\Software{IPANEMAP}}
\newcommand{\Start}{s}
\newcommand{\End}{e}

\newcommand{\yp}[1]{{\todo[color=blue!30]{\sf Yann: #1}}}

@@

\section{ Cordero~\emph{et al} dataset}
\subsection{Structure prediction ordered by RNA}

 \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[h]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}
 &\multicolumn{8}{l}{ \OurTool{}} & \multicolumn{4}{l}{ RNAfold MFE} & \multicolumn{4}{l}{RNAfold MEA} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\
\toprule
\textbf{RNA }& \multicolumn{1}{l}{(-)} & \multicolumn{1}{l}{CMCT} & \multicolumn{1}{l}{NMIA} & \multicolumn{1}{l}{DMS} & \multicolumn{1}{l}{DMS+NMIA} & \multicolumn{1}{l}{DMS+CMCT}& \multicolumn{1}{l}{NMIA+CMCT}	 & \multicolumn{1}{l}{DMS+NMIA+CMCT} & \multicolumn{1}{l}{(-)}& \multicolumn{1}{l}{DMS }& \multicolumn{1}{l}{CMCT} &\multicolumn{1}{l}{ NMIA}& \multicolumn{1}{l}{(-)} & \multicolumn{1}{l}{DMS} & \multicolumn{1}{l}{CMCT} & \multicolumn{1}{l}{NMIA}\\
\midrule
5SRNA,E.Coli		&	0.25	&	0.238	&	0.247	&	0.244	&	0.247	&	0.247	&	0.254	&	0.241	&	0.241	&	0.686	&	0.254	&	0.686	&	0.241	&	0.686	&	0.269	&	0.686	\\
glycineriboswitch,F.nucleatum		&	0.568	&	0.627	&	0.868	&	0.952	&	0.868	&	0.658	&	0.868	&	0.868	&	0.306	&	0.313	&	0.395	&	0.313	&	0.593	&	0.593	&	0.693	&	0.6	\\
cidGMPriboswitch,V.Cholerae		&	0.654	&	0.77	&	0.654	&	0.77	&	0.654	&	0.77	&	0.654	&	0.77	&	0.77	&	0.77	&	0.667	&	0.77	&	0.77	&	0.72	&	0.667	&	0.77	\\
P4P6domain		&	0.864	&	0.856	&	0.881	&	0.864	&	0.864	&	0.856	&	0.864	&	0.856	&	0.837	&	0.808	&	0.773	&	0.714	&	0.845	&	0.808	&	0.781	&	0.722	\\
adenineriboswitch,add		&	1	&	0.956	&	1	&	0.977	&	1	&	0.956	&	1	&	1	&	1	&	0.333	&	0.41	&	1	&	1	&	0.333	&	0.356	&	0.306	\\
tRNAphenylalanineyeast		&	0.286	&	0.746	&	0.976	&	0.746	&	0.976	&	0.746	&	0.976	&	0.976	&	0.976	&	0.976	&	0.976	&	0.976	&	0.334	&	0.976	&	0.976	&	0.976	\\

\midrule
Average&0.604&0.7&0.77&0.76&0.77&0.705&0.77&0.785&0.69&0.65&0.58&0.74&0.63&0.69&0.62&0.68\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{ GM of the predicted structures with \OurTool{} compared to RNAfold MFE and MEA resulting structures}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection{Reproducibility}
\begin{table}[h]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\
\toprule
\textbf{RNA }& \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3} & \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3}& \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3} & \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3}& \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3} & \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3}& \multicolumn{1}{l}{run 1} & \multicolumn{1}{l}{run 2} & \multicolumn{1}{l}{run 3}\\
\midrule
5SRNA,E.Coli	&	0.247	&	0.25	&	0.247	&	0.254	&	0.244	&	0.244	&	0.238	&	0.238	&	0.238	&	0.247	&	0.244	&	0.247	&	0.257	&	0.238	&	0.238	&	0.247	&	0.247	&	0.244	&	0.241	&	0.241	&	0.241	\\
glycineriboswitch,F.nucleatum	&	0.868	&	0.868	&	0.868	&	0.952	&	0.952	&	0.952	&	0.868	&	0.634	&	0.627	&	0.868	&	0.868	&	0.868	&	0.868	&	0.868	&	0.868	&	0.667	&	0.658	&	0.658	&	0.868	&	0.868	&	0.868	\\
cidGMPriboswitch,V.Cholerae	&	0.631	&	0.631	&	0.631	&	0.77	&	0.77	&	0.77	&	0.667	&	0.77	&	0.77	&	0.631	&	0.631	&	0.756	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	\\
P4P6domain	&	0.864	&	0.881	&	0.881	&	0.864	&	0.864	&	0.856	&	0.856	&	0.856	&	0.856	&	0.864	&	0.864	&	0.864	&	0.864	&	0.864	&	0.864	&	0.856	&	0.856	&	0.856	&	0.856	&	0.856	&	0.856	\\
adenineriboswitch,ad	&	1	&	1	&	1	&	0.956	&	0.956	&	0.956	&	1	&	0.956	&	0.956	&	1	&	1	&	1	&	1	&	1	&	1	&	0.956	&	0.956	&	0.956	&	1	&	1	&	1	\\
tRNAphenylalanineyeast	&	0.953	&	0.953	&	0.976	&	0.976	&	0.746	&	0.976	&	0.746	&	0.746	&	0.746	&	0.976	&	0.976	&	0.976	&	0.976	&	0.976	&	0.97	&	0.746	&	0.746	&	0.746	&	0.746	&	0.976	&	0.976	\\

@@

%\section{IPANEMAP Vs Rsample}
\section{Hadjin ~\emph{et al} dataset}

  \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llllHllH}
\toprule
\textbf{RNA} & Length &  \multicolumn{3}{l}{\Software{Rsample}} &  \multicolumn{3}{l}{\Software{IPANEMAP}} \\
\midrule
	&		&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	\\
A	&	34	&	0.625	&	1	&	0.791	&	0.625	&	1	&	0.791	\\
B	&	530	&	0.6622	&	0.6203	&	0.641	&	0.8986	&	0.8062	&	0.851	\\
C	&	301	&	0.03	&	0.0313	&	0.031	&	0.6	&	0.6	&	0.6	\\
D	&	214	&	0.6349	&	0.6667	&	0.651	&	0.7302	&	0.8519	&	0.789	\\
E	&	500	&	0.6382	&	0.7823	&	0.707	&	0.5263	&	0.5517	&	0.539	\\
F	&	47	&	0.4	&	0.75	&	0.548	&	0.6	&	0.75	&	0.671	\\
G	&	118	&	0.7179	&	0.8	&	0.758	&	0.7692	&	0.8333	&	0.801	\\
H	&	76	&	0.4762	&	0.5556	&	0.514	&	0.7619	&	0.7619	&	0.762	\\
I	&	155	&	0.6786	&	0.8261	&	0.749	&	0.9821	&	0.9821	&	0.982	\\
J	&	79	&	0.7727	&	0.85	&	0.81	&	0.9545	&	0.875	&	0.914	\\
K	&	71	&	1	&	1	&	1	&	1	&	0.9545	&	0.977	\\
L	&	66	&	0.5625	&	0.6923	&	0.624	&	0.625	&	0.7143	&	0.668	\\
M	&	79	&	0.6538	&	0.8095	&	0.727	&	0.6538	&	0.68	&	0.667	\\
N	&	120	&	0.2857	&	0.2632	&	0.274	&	0.9714	&	0.9189	&	0.945	\\
O	&	97	&	0.9286	&	0.9286	&	0.929	&	0.9286	&	0.8966	&	0.912	\\
P	&	511	&	0.9328	&	0.7762	&	0.851	&	0.8908	&	0.7681	&	0.827	\\
Q	&	401	&	0.5826	&	0.5583	&	0.57	&	0.7304	&	0.75	&	0.74	\\
R	&	425	&	0.8397	&	0.8271	&	0.833	&	0.9084	&	0.8815	&	0.895	\\
S	&	336	&	0.5481	&	0.6129	&	0.58	&	0.8077	&	0.866	&	0.836	\\
T	&	473	&	0.7986	&	0.7143	&	0.755	&	0.8819	&	0.8194	&	0.85	\\
U	&	412	&	0.5379	&	0.6174	&	0.576	&	0.75	&	0.8462	&	0.797	\\
V	&	75	&	0.619	&	0.6842	&	0.651	&	0.619	&	0.5652	&	0.591	\\
W	&	174	&	0.8095	&	0.8644	&	0.836	&	0.8095	&	0.9808	&	0.891	\\
X	&	154	&	0.875	&	0.913	&	0.894	&	0.875	&	0.913	&	0.894	\\

\bottomrule
\end{tabular}
\end{adjustbox}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

 \begin{table}[h]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}ll@{}}
 \toprule
Rna ID & Description\\
 \midrule
A	&	PreQ1riboswitchBsubtilis\\
B	&	5domainof16SrRNAEcoli\\
C	&	SignalrecognitonparticleRNAhuman\\
D	&	GroupIintronAzoarcussp\\
E	&	HIV15primepseudoknotdomain\\
F	&	Telomerasepseudoknothuman\\
G	&	SAMIriboswitchTtengcongensis\\
H	&	tRNApheEcoli\\
I	&	P546domainbI3groupIintron\\
J	&	TPPriboswitchEcoli\\
K	&	AdenineriboswitchVvulnificus\\
L	&	FluorideriboswitchPsyringae\\
M	&	SARScoronaviruspseudoknot\\
N	&	5SrRNAEcoli\\
O	&	cyclicdiGMPriboswitchVcholerae\\
P	&	5domainof23SrRNAEcoli\\
Q	&	RNasePBsubtilis\\
R	&	GroupIIntronTthermophila\\
S	&	HepatitisCvirusIRESdomain\\
T	&	5domainof16SrRNAHvolcanii\\
U	&	GroupIIintronOiheyensis\\
V	&	tRNAaspyeast\\
W	&	LysineriboswitchTmaritime\\
X	&	MBoxriboswitchBsubtilis\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{24 RNAs from Hadjin \emph{ et al.} dataset.}
\label{clyu}

\end{table}
%  \Heatset{min=0,  
%	max=1,   
%	max colour=Aquamarine3, % colour at maximum
%	min colour=BadCol,      % colour at minimum
%	Min colour=BadCol, % colour for values below min
%	Max colour=Aquamarine3   % colour for values above max
%}

\begin{table}
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llHHHHHHHHHHHlHH}
\toprule
\textbf{RNA} & Length &  \multicolumn1c{Run1} &\multicolumn1c{Run2}&\multicolumn1c{Run3}&\multicolumn1c{Run4}&\multicolumn1c{Run5}&\multicolumn1c{Run6}&\multicolumn1c{Run7}&\multicolumn1c{Run8}&\multicolumn1c{Run9}&\multicolumn1c{Run10}& \multicolumn1c{Average}& \multicolumn1c{Sd}&\multicolumn1c{\textbf{MFE-RNAfold}} & \multicolumn1c{\textbf{MEA-RNAfold}}\\
\midrule

@@

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{adjustbox}   
%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%%%%%%%%%%%%%%%%%%%%%%%%%formatting cells colors
\usepackage[table,x11names,dvipsnames]{xcolor}
 \usepackage{collcell}
 \usepackage{array}
 \usepackage{tikz}
 \usepackage{relsize}
  \usepackage{pgfkeys}
 \usepackage{graphicx}
 \usepackage{xspace}
 \usepackage{amsmath,amssymb}

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{inconsolata}

\input{macros.tex}

\title{\OurTool{}:  Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em]
	Supplementary material
}
\author{}
\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed 
\newcommand{\Start}{s}
\newcommand{\End}{e}

@@

\section{Detailed results on Cordero~\emph{et al} dataset}
\subsection{Structure prediction ordered by RNA}

 \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection{Reproducibility}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

Replicates& \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3} & \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3}& \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3} & \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3}& \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3} & \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3}& \multicolumn{1}{l}{Run 1} & \multicolumn{1}{l}{Run 2} & \multicolumn{1}{l}{Run 3}\\
\midrule
5SRNA,E.Coli	&	0.247	&	0.25	&	0.247	&	0.254	&	0.244	&	0.244	&	0.238	&	0.238	&	0.238	&	0.247	&	0.244	&	0.247	&	0.257	&	0.238	&	0.238	&	0.247	&	0.247	&	0.244	&	0.241	&	0.241	&	0.241	\\
glycineriboswitch,F.nucleatum	&	0.868	&	0.868	&	0.868	&	0.952	&	0.952	&	0.952	&	0.868	&	0.634	&	0.627	&	0.868	&	0.868	&	0.868	&	0.868	&	0.868	&	0.868	&	0.667	&	0.658	&	0.658	&	0.868	&	0.868	&	0.868	\\
cidGMPriboswitch,V.Cholerae	&	0.631	&	0.631	&	0.631	&	0.77	&	0.77	&	0.77	&	0.667	&	0.77	&	0.77	&	0.631	&	0.631	&	0.756	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	&	0.77	\\
P4P6domain	&	0.864	&	0.881	&	0.881	&	0.864	&	0.864	&	0.856	&	0.856	&	0.856	&	0.856	&	0.864	&	0.864	&	0.864	&	0.864	&	0.864	&	0.864	&	0.856	&	0.856	&	0.856	&	0.856	&	0.856	&	0.856	\\
adenineriboswitch,ad	&	1	&	1	&	1	&	0.956	&	0.956	&	0.956	&	1	&	0.956	&	0.956	&	1	&	1	&	1	&	1	&	1	&	1	&	0.956	&	0.956	&	0.956	&	1	&	1	&	1	\\
tRNAphenylalanineyeast	&	0.953	&	0.953	&	0.976	&	0.976	&	0.746	&	0.976	&	0.746	&	0.746	&	0.746	&	0.976	&	0.976	&	0.976	&	0.976	&	0.976	&	0.97	&	0.746	&	0.746	&	0.746	&	0.746	&	0.976	&	0.976	\\

@@

\newpage

%\section{IPANEMAP Vs Rsample}
\section{Detailed results on Hadjin~\emph{et al} dataset}

 \begin{table}[h]

{\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}llll@{}}
 	\toprule
 	RNA ID & Description                      \\ \midrule
 	A      & PreQ1riboswitchBsubtilis         & 	M      & SARScoronaviruspseudoknot        \\
 	B      & 5domainof16SrRNAEcoli            & 	N      & 5SrRNAEcoli                      \\
 	C      & SignalrecognitonparticleRNAhuman & 	O      & cyclicdiGMPriboswitchVcholerae   \\
 	D      & GroupIintronAzoarcussp           & 	P      & 5domainof23SrRNAEcoli            \\
 	E      & HIV15primepseudoknotdomain       & 	Q      & RNasePBsubtilis                  \\
 	F      & Telomerasepseudoknothuman        & 	R      & GroupIIntronTthermophila         \\
 	G      & SAMIriboswitchTtengcongensis     & 	S      & HepatitisCvirusIRESdomain        \\
 	H      & tRNA phe Ecoli                   & 	T      & 5domainof16SrRNAHvolcanii        \\
 	I      & P546domainbI3groupIintron        & 	U      & GroupIIintronOiheyensis          \\
 	J      & TPPriboswitchEcoli               & 	V      & tRNAaspyeast                     \\
 	K      & AdenineriboswitchVvulnificus     & 	W      & LysineriboswitchTmaritime        \\
 	L      & FluorideriboswitchPsyringae      & 	X      & MBoxriboswitchBsubtilis          \\
 	\bottomrule
 \end{tabular}
\end{adjustbox}\\}

\caption{Labels used for the 24 RNAs in the Hadjin \emph{ et al.} dataset~\cite{Hajdin2013}.}
\label{clyu}

\end{table}

\begin{table}[H]
	\begin{adjustbox}{max width=1\textwidth,max totalheight=\textheight,keepaspectratio}
		\begin{tabular}{llHHHHHHHHHHHlHH}
			\toprule
			\textbf{RNA} & Length &  \multicolumn1c{Run1} &\multicolumn1c{Run2}&\multicolumn1c{Run3}&\multicolumn1c{Run4}&\multicolumn1c{Run5}&\multicolumn1c{Run6}&\multicolumn1c{Run7}&\multicolumn1c{Run8}&\multicolumn1c{Run9}&\multicolumn1c{Run10}& \multicolumn1c{Average}& \multicolumn1c{Sd}&\multicolumn1c{\textbf{MFE-RNAfold}} & \multicolumn1c{\textbf{MEA-RNAfold}}\\
			\midrule

@@

\Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
{\centering \begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llllHllH}
	\toprule
	      &        & \multicolumn{3}{l}{\Software{Rsample}}    & \multicolumn{3}{l}{\Software{IPANEMAP}}   \\
	{RNA} & Length & Sensitivity & PPV    & \multicolumn1c{GM} & Sensitivity & PPV    & \multicolumn1c{GM} \\ \midrule
	A     & 34     & 0.625       & 1      & 0.791              & 0.625       & 1      & 0.791              \\
	B     & 530    & 0.6622      & 0.6203 & 0.641              & 0.8986      & 0.8062 & 0.851              \\
	C     & 301    & 0.03        & 0.0313 & 0.031              & 0.6         & 0.6    & 0.6                \\
	D     & 214    & 0.6349      & 0.6667 & 0.651              & 0.7302      & 0.8519 & 0.789              \\
	E     & 500    & 0.6382      & 0.7823 & 0.707              & 0.5263      & 0.5517 & 0.539              \\
	F     & 47     & 0.4         & 0.75   & 0.548              & 0.6         & 0.75   & 0.671              \\
	G     & 118    & 0.7179      & 0.8    & 0.758              & 0.7692      & 0.8333 & 0.801              \\
	H     & 76     & 0.4762      & 0.5556 & 0.514              & 0.7619      & 0.7619 & 0.762              \\
	I     & 155    & 0.6786      & 0.8261 & 0.749              & 0.9821      & 0.9821 & 0.982              \\
	J     & 79     & 0.7727      & 0.85   & 0.81               & 0.9545      & 0.875  & 0.914              \\
	K     & 71     & 1           & 1      & 1                  & 1           & 0.9545 & 0.977              \\
	L     & 66     & 0.5625      & 0.6923 & 0.624              & 0.625       & 0.7143 & 0.668              \\
	M     & 79     & 0.6538      & 0.8095 & 0.727              & 0.6538      & 0.68   & 0.667              \\
	N     & 120    & 0.2857      & 0.2632 & 0.274              & 0.9714      & 0.9189 & 0.945              \\
	O     & 97     & 0.9286      & 0.9286 & 0.929              & 0.9286      & 0.8966 & 0.912              \\
	P     & 511    & 0.9328      & 0.7762 & 0.851              & 0.8908      & 0.7681 & 0.827              \\
	Q     & 401    & 0.5826      & 0.5583 & 0.57               & 0.7304      & 0.75   & 0.74               \\
	R     & 425    & 0.8397      & 0.8271 & 0.833              & 0.9084      & 0.8815 & 0.895              \\
	S     & 336    & 0.5481      & 0.6129 & 0.58               & 0.8077      & 0.866  & 0.836              \\
	T     & 473    & 0.7986      & 0.7143 & 0.755              & 0.8819      & 0.8194 & 0.85               \\
	U     & 412    & 0.5379      & 0.6174 & 0.576              & 0.75        & 0.8462 & 0.797              \\
	V     & 75     & 0.619       & 0.6842 & 0.651              & 0.619       & 0.5652 & 0.591              \\
	W     & 174    & 0.8095      & 0.8644 & 0.836              & 0.8095      & 0.9808 & 0.891              \\
	X     & 154    & 0.875       & 0.913  & 0.894              & 0.875       & 0.913  & 0.894              \\ \bottomrule
\end{tabular}
\end{adjustbox}\\}

\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

%  \Heatset{min=0,  
%	max=1,   
%	max colour=Aquamarine3, % colour at maximum
%	min colour=BadCol,      % colour at minimum
%	Min colour=BadCol, % colour for values below min
%	Max colour=Aquamarine3   % colour for values above max
%}
